---
name: "Connor Smith"
date: "`r format(Sys.time(), '%B %Y')`"
position: "Informatics Research Associate"
qualifications: MS, BS
address: Department of Medical Informatics & Clinical Epidemiology, Oregon Health & Science University
phone: +1 503-347-0726
email: smitco@ohsu.edu
twitter: ConnorJPSmith
github: ConnorJPSmith
linkedin: ConnorJPSmith
headcolor: 5E97C9
output: vitae::awesomecv
---
<!-- NOTE: awesomecv requires you to flip the WHAT and WITH arguements, otherwise it looks weird -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(rorcid)
library(lubridate)
library(tools)
library(glue)
```

```{r prep_data, include=FALSE, warning=FALSE}
# jobs
jobs <- read_csv(file = '../data/jobs.csv') %>%
  # short format, exclude long records
  mutate(format = case_when(is.na(format) | format == 'short' ~ 'short',
                            TRUE ~ 'long')) %>%
  filter(format == 'short') %>%
  mutate(start = mdy(start),
         end = mdy(end),
         period = case_when(is.na(end) ~ paste0(year(start), '-Present'),
                            year(start) == year(end) ~ as.character(year(start)),
                            TRUE ~ paste0(year(start),'-',year(end)))) %>%
  arrange(desc(start)) #arrange(!is.na(end),desc(start)) #to have current jobs shown first
jobs_desc <- jobs %>% 
  inner_join(y = read_csv(file = '../data/jobs_desc.csv'),
             by = 'jobId')

# presentations
presentations <- read_csv(file = '../data/presentations.csv') %>%
  mutate(date = mdy(date))

# professional development
profDevel <- read_csv(file = '../data/professionalDevelopment.csv') %>%
  mutate(date = mdy(date))

# awards/honors
awards <- read_csv(file = '../data/awards_grants.csv') %>%
  mutate(date = mdy(date))
```

```{r update_bib}
# manual entries
thesis <- tribble(
  ~bibtype, ~author, ~title, ~school, ~year, ~key,
  'MastersThesis', 
  'Connor J Smith', 
  'Hypermethylation in the promoter of PRDM16 is associated with decreased survival in AML patients', 
  'OHSU', 
  2019, 
  'MSBioinformatics'
)

inPress <- tribble(
  ~bibtype, ~author, ~title, ~journaltitle, ~year, ~key,
  'Customa', 'Connor J Smith, Rebecca M Jungbauer, Annette M Totten', 'Special Section on Visual Analytics in Healthcare: Visual Evidence: Increasing Usability of Systematic Reviews in Health Systems Guidelines Development', 'Applied Clinical Informatics',2019, 'aciSpecialSectionVAHC',
  'Customa', 'KF Sarmiento, RL Folmer, CJ Stepnowsky, MA Whooley, EA Boudreau, ST Kuna, CW Atwood, CJ Smith, WC Yarbrough', 'National Expansion of Sleep Telemedicine for Veterans: The TeleSleep Program', 'J Clinical Sleep Medicine', 2019, 'jcsmTeleSleep'
)


published <- scholar::get_publications("H45dNhoAAAAJ") %>% 
  #filter(cites > 30) %>% 
  distinct(title, .keep_all = TRUE) %>%
  transmute(bibtype = "Article", 
            author = as.character(author),
            title = as.character(title),
            journaltitle = as.character(journal), 
            year, 
            key = glue('published_{row_number()}'))


# write to bib
bib <- thesis %>%
  union_all(inPress) %>%
  union_all(published) %>% 
  RefManageR::as.BibEntry() %>%
  RefManageR::WriteBib("smith.bib")

```


# Education

```{r education}
tribble(
  ~Degree, ~Dates, ~School, ~Location,
  'Masters of Science in Biomedical Informatics', '2016-2019', 'Oregon Health & Science University', 'Portland, OR',
  'Bachelors of Science in Biology', '2010-2014', 'Oregon State University', 'Corvallis, OR') %>% 
  detailed_entries(
    what = School,
    when = Dates, 
    with = Degree,
    where = Location
  )
```

# Employment  
```{r jobs}
jobs_desc %>%
  filter(type != 'military') %>%
  detailed_entries(what = employer,
                   when = period,
                   with = position,
                   where = glue('{city}, {state}'),
                   why = accomplishment)

```  

## Military  
```{r military}
jobs_desc %>%
  filter(type == 'military') %>%
  detailed_entries(what = employer,
                   when = period,
                   with = position,
                   where = glue('{city}, {state}'),
                   why = accomplishment)

```

# Relevant Skills
\begin{cvskills}
  \cvskill {Applications} {RStudio; Microsoft SQL Server Management Studio; Tableau; Anaconda; Toad; Oracle Application Express (APEX); Neo4J}
  \cvskill {Databases} {Relational database theory, development, management; Non-relational databases; Graph databases}
  \cvskill {Languages} {R; SQL; PL/SQL; Python; HTML; CSS; LaTex; Cypher}
  \cvskill {Data Science} {Supervised and unsupervised machine learning; Data wrangling; Data visualization; Process automation}
\end{cvskills}

# Awards and Honors  
```{r awards}
awards %>%
  brief_entries(what = glue('{award} - {from}'),
                when = glue('{month(date, label = TRUE)} {year(date)}'),
                with = organization)

```

\newpage  
# Publications

## Articles  
```{r articles}
bibliography_entries("smith.bib") %>%
  filter(bibtype == 'Article')
```  

## Master's Thesis  
```{r thesis}
bibliography_entries("smith.bib") %>%
  filter(bibtype == 'MastersThesis')
``` 

## Working Publications Under Review  
```{r inProgress}
bibliography_entries("smith.bib") %>%
  filter(bibtype == 'Customa')
```

# Presentations  

## Talks  
```{r presentations_talks}
presentations %>%
  filter(type == 'talk') %>% 
  arrange(desc(date)) %>% 
  detailed_entries(what = event,
                   when = glue('{month(date, label = TRUE)} {year(date)}'),
                   with = title,
                   where = glue('{city}, {state}')
                   )
```

## Workshops  
```{r presentations_workshops}
presentations %>%
  filter(type == 'workshop') %>% 
  arrange(desc(date)) %>% 
  detailed_entries(what = event,
                   when = glue('{month(date, label = TRUE)} {year(date)}'),
                   with = title,
                   where = glue('{city}, {state}')
                   )
```  

## Competitions  
```{r presentations_comp}
presentations %>%
  filter(type == 'design challenge') %>% 
  arrange(desc(date)) %>% 
  detailed_entries(what = event,
                   when = glue('{month(date, label = TRUE)} {year(date)}'),
                   with = title,
                   where = glue('{city}, {state}'),
                   why = award)
```

\newpage
# Service  

**Manuscript Reviews**  

- Applied Clinical Informatics (2)  

# Professional Development  
```{r profDevel}
profDevel %>% 
  arrange(desc(date)) %>% 
  detailed_entries(what = glue('{tools::toTitleCase(type)} hosted by {sponsor}'),
                   when = date,
                   with = title,
                   where = glue('{city}, {state}')
                   )
```
